---
title: "Allen's Play with RMD File"
author: "Allen Pannell"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
child: "Child.rmd"
---

Other options can go above ????????????????

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) ## Set's the defaults

## knitr::include_rmd("Child.rmd")
```

## R Markdown  [RMD Help](https://yihui.org/knitr/options/)


Below are a few more tips about chunk options:

The chunk header must be written on one line. You must not break the line.

Try to avoid spaces, periods (.), and underscores (_) in chunk labels and paths. If you need separators, you are recommended to use hyphens (-) instead. For example, setup-options is a good label, whereas setup.options and chunk 1 are bad; fig.path = 'figures/mcmc-' is a good path for figure output, and fig.path = 'markov chain/monte carlo' is bad.

```{r cars, echo=TRUE}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
